Trygve's Problem

### 2018-03-23 trygve/outline.tex
Added widths information

There is one possibly confusing aspect of our output that we would like to to address.  The upper and lower bounds (as we have visualized them) are each actually impossible as values for $q$.  For example, the rows of the upper bounds generally sum to more than 1.  This is because we have taken \emph{elementwise bounds} on each entry.  An alternative is to  sample uniformly from the set of possible values of $q$ which are consistent with our observations.  We hope this may give the user another way to understand what possible values $q$ might take on.

To this end, we use a Dikin ellipsoid sampler to approximate uniform samples from the set of valid $q$s which are consistent with what we've observed.  These are shown in Figure \ref{fig:allenavg}.  Whether the MCMC method is mixing or not is of course up for debate.  See Appendix \ref{sec:dikin} for some details.

@@

>>>>

Note that the upper and lower bounds (as we have visualized them) are each actually impossible as values for $q$.  For example, the rows of the upper bounds generally sum to more than 1.  This is because we have taken \emph{elementwise bounds} on each entry.  An alternative is to  sample uniformly from the set of possible values of $q$ which are consistent with our observations.  We hope this may give the user another way to understand what possible values $q$ might take on.  To this end, we use a Dikin ellipsoid sampler to approximate uniform samples from the set of valid $q$s which are consistent with what we've observed.  These are shown in Figure \ref{fig:allenavg}.  Whether the MCMC method is mixing or not is of course up for debate.  See Appendix \ref{sec:dikin} for some details.

Another way to look at the space of possible values of $q$ which are consistent with the observables is to look at the width of the polytope in various directions.  That is, select a direction uniformly at random, and measure the width of the polytope along that direction.  Note that this is not at all the same as selecting a random direction and seeing how far one can travel before hitting any boundary; obtaining the full width in a given direction requires solving a linear program.  Doing this procedure many times and taking a histogram yields Figure \ref{fig:allenwidths}.  This suggests that the polytope may be only about 7 units in length; distributed over 1624 entries of the matrix, each of which lies in $[0,1]$; this suggests that the polytope may indeed be  constrained to be close to the output we showed in Figure \ref{fig:allenoutput}.

@@

\begin{figure}
\includegraphics[width=0.8\textwidth]{pics/allenwidths}
\caption{Allen institute data: the width of the polytope.\label{fig:allenwidths}}
\end{figure}
